\documentclass{acm_proc_article-sp}

\usepackage{url}

\numberofauthors{3}
\author{
  \alignauthor
  Charlie Moore\\
  \email{cmoore@nmt.edu}
  \alignauthor
  Thomas Coppi\\
  \email{tcoppi@nmt.edu}
  \alignauthor
  Aaron Lovato\\
  \email{alovato@nmt.edu}
}
\title{BitTorrent Reconstitutor Project Brief}

\begin{document}
\maketitle
\begin{abstract}
This is an overview of the research and forensic impacts of our project.
\end{abstract}
%\keywords{}

% Paper stuff starts here

\section{Introduction}
\subsection{Functionality}
The application will identify and reconstruct any files transferred using the
BitTorrent protocol from network traffic. It can be run against both live input
and stored packet capture (pcap) files. It will take as input either a network
interface (for live input) or a pcap file and a list of \texttt{.torrent}
files. The \texttt{.torrent} files are necessary for verification of files found
in the network traffic; however, all files will be reconstructed, not just those
that can be verified. The application will produce the files as output along
with data pertaining to the transfer of the files as well as whether each file
was verified.

Specifically, this application will perform the following tasks: identify files,
reconstruct them, log information about the file transfer, and verify the
integrity of the file based on a \texttt{.torrent} file (if provided). It will not
perform any processing or analysis of the files other than that which is
necessary for identification and reconstruction of the files. Other applications
and/or manual analysis will be needed to process the files separately from this
application.

\section{Threat Model}
Threats this application can be used to mitigate include transfer of contraband
using BitTorrent, analysis of network traffic from an incident in which
BitTorrent was used to transfer files to a compromised host, and detection of
data exfiltration where BitTorrent is used to break the file(s) into smaller
pieces that may evade detection from file scanning utilities. Note that the
last case is one in which the application would be run against live traffic
while the first two would require offline processing of packet capture files.

\section{Forensics Impact}
This application will give analysts the ability to extract files transferred
using BitTorrent from network traffic. While tools (such as virus scanners) and
techniques (such as reverse engineering) are currently available and used to
analyze files, no publicly available application exists to reconstruct files
transferred over the BitTorrent protocol. This application is designed simply to
fill the gap in retrieving capabilities rather than extending any analysis
capability.

As noted in the threat model, most uses for this application will result in
processing of offline data. Accordingly, the main context for usage of this
application will be post-incident analysis, after packets captures have been
collected. However, some uses in which the application is processing live input
can be used to initially identify an incident rather than respond to a known
incident.

\subsection{Future}
As a possible future extension, DHT (distributed hash table) is close
to becoming standardized and is currently in use by many big BitTorrent names.
DHT makes it so that we don't have to use trackers and distributors to get the
peer and metadata information.  Torrent files can be distributed through the
DHT, which has a big impact on our program.  As of now, we're assuming that the
torrent file has to somehow magically be captured separately from the BitTorrent
traffic.  If we can incorporate DHT technology into our program, we can
eliminate this constraint.

\section{Conclusion}


% Add References
\bibliographystyle{plain}
%\bibliography{refs}
\balancecolumns
\end{document}
